% Last Modification:
% @author AUTHOR_NAME
% @date TODAY_DATE

\chapter{Introduction}
\label{chap:introduction}

\section{Overview}
Motivation for creating this Specification report is that iCrash CMS system has
been updated recently. In this new version we have to cover the main changes and
their affects on the other modules of the system. \\
This Specification report should be considered as the only true. Because
previous versions doesn`t consider actual featrues of current version of iCrash system
and there is no other actual version except this neither printed nor the online
help. This document provides minimum acceptable information for knowing how to
use iCrash. \\
This Specification report is limited to the software documentation product and
does not include the processes of developing or managing software user documentation. It does not apply to specialized course materials
intended primarily for use in formal training programs. \\

\section{Purpose and recipients of the document}
The aim of this document is to provide an example of how the design of a
particular software system should be documented.

The recipient of this document is the development company (ADC) in charge
of delivering the software system. The company's developers are
expected to use this document as the basis for carrying out the actual
development and deployment of the product (i.e. implementation, testing
and maintenance).

 
\section{Application Domain}
iCrash system is dedicated to inform about a car crash and help with crisis
handling. The purpose of this application is to take control over emergency
situations, optimize the process of their resolving, to provide mechanism of
centralized information gathering from any person involved in car crash crisis
and to guide victims during crisis handling.
 
\section{Definitions, acronyms and abbreviations}

\subsubsection{Activator}
Represents a logical actor for time automatic message sending based on system’s
or environment status.\\
Functionalities:
\begin{itemize}
  \item Communication of the current time to the system
  \item Notification of the administrator that some crisis are still pending for
  a too long time
\end{itemize}

\subsubsection{Administrator}
Represents an actor responsible of administration tasks for the iCrash system.\\
Functionalities:
\begin{itemize}
  \item Adding coordinator actors to the system and its environment
  \item Deleting coordinator actors from the system and its environment
\end{itemize}

\subsubsection{Communication Company}
Represents the communication company stakeholder ensuring the input/ouput of
textual messages with humans having communication devices.\\
Functionalities:
\begin{itemize}
  \item Delivery of any SMS sent by any human to the iCrash's phone number
  \item Transmission of SMS messages from the ABC company that owns the iCrash
  system to any human having an SMS compatible device accessible using a phone
  number
\end{itemize}

\subsubsection{Coordinator}
Represents actor responsible of handling one or several crisis for the iCrash
system.\\
Functionalities:
\begin{itemize}
  \item Securely monitoring the existing alerts and crisis
  \item Securely managing alerts and crisis until their termination
\end{itemize}

\subsubsection{Messir Creator}
Represents the creator stakeholder in charge of state and environment
initialization.\\
Functionalities:
\begin{itemize}
  \item Installation of the iCrash System
  \item Definition of the values for the initial system’s state
  \item Definition of the values for the initial system’s environment
  \item Ensurance of  the integration of the iCrash system with its initial
  environment
\end{itemize}

\section{Document structure} 
