% Last Modification:
% @author AUTHOR_NAME
% @date TODAY_DATE

\chapter{General Description}
In the context of the \msrmessir method, the information provided in this
section is intended to present the system for which the \msrmessir analysis is
provided. The content of this section is made accordingly to the requirements
elicitation document that might have been done during the project but also
adapted coherently in order to be an abstract introduction to the \msrmessir
analysis.

\section{Domain Stakeholders}
All stakeholders of the system are detailed in this section. After a brief
description of a stakeholder, its objectives are first stated. Thereafter, the
responsibilities of the stakeholder are detailed which help to achieve the
stakeholder objectives to a certain degree. While the objectives characterize
the general problems addressed by the \msrprojectname system, the responsibilities
describe concrete actions that are expected from a stakeholder. All stakeholders
listed in this section have an interest in the system or are affected by the
system in some way, but only a subset of the stakeholders are directly involved
in the use cases described. Let us remind that use case diagrams or descriptions
are not Messir analysis phase mandatory outputs. They are proposed as informal
means to help understanding the semantics of the system specification made of
the mandatory analysis models, which provide a complete executable
specification.

\subsection{Communication Company}
A Communication Company is a company that has the capacity to ensure
communication of information between its customers and the \msrprojectname system. The
objectives of a Communication Company are:
\begin{itemize}
\item to be able to deliver any SMS sent by any human to the \msrprojectname's phone
number.
\item to be able to transmit SMS messages from the ABC company that owns the
\msrprojectname system to any human having an SMS compatible device accessible using a
phone number.
\end{itemize}
In order to achieve these objectives, the responsibilities of a Communication
Company are:
\begin{itemize}
\item ensure confidentiality and integrity of the information sent by a human
to the \msrprojectname system or from the system to a human.
\item to be always available and reliable.
\end{itemize}
\subsection{Humans}
A human is any person who considers himself related to a car crash either as a
witness, a victim or an anonymous person. The objectives of a human are:
\begin{itemize}
\item inform the \msrprojectname system about the crisis situation he detected.
\item be sure that the ABC company has been informed about the situation.
\item to be informed about the situation of the crisis he his related to as a
 victim or witness.
\end{itemize}
In order to achieve these objectives, the responsibilities of a human are:
\begin{itemize}
\item to provide has much details as possible concerning the crisis to the ABC
 company.
\item  to declare a crisis only if the crisis is real.
\item  to have access to the SMS compatible communication device he used to
 communication with the
\end{itemize}
\msrprojectname system.
\subsection{Coordinators}
A coordinator is a employee of the ABC company being responsible of handling one
or several crisis. The objectives of a coordinator are:
\begin{itemize}
\item   to securely monitor the existing alerts and crisis.
\item   to securely manage alerts and crisis until their termination.
\end{itemize}
In order to achieve these objectives, the responsibilities of a coordinator are:
\begin{itemize}
\item   to be capable to determine how an alert received should be considered.
\item   to be available to react to requests to handle alerts and crisis.
\item   to be autonomous in handling crisis and to report on its handling.
\item   to be able to decide when a crisis or an alert can be closed.
\item   to know its system identification information for secure usage of the
system.
\end{itemize}
\subsection{Administrator}
An administrator is a employee of the ABC company being responsible of
administrating the \msrprojectname system. The objectives of an administrator are:
\begin{itemize}
\item    to add or delete coordinator actors from the system and its
 environment.
\end{itemize}
In order to achieve these objectives, the responsibilities of a coordinator are:
\begin{itemize}
\item    know the company employees that can be coordinators and that have
 access to the system.
\item    to know its system identification information for secure usage of the
 system.
\item    to know the security policy of the ABC company.
\item    to communicate the coordinators their identification information for
 secure system usage.
\end{itemize}

\subsection{Creator}
Any system has a Creator stakeholder which is a technician who is installing the
\msrprojectname system on the targeted deployment infrastructure. The objectives of a
Creator are:
\begin{itemize}
	\item to install the \msrprojectname system
	\item to define the values for the initial system's state
	\item to define the values for the initial system's environment
	\item to ensure the integration of the \msrprojectname system with its initial
	environment
\end{itemize}
In order to achieve these objectives, the responsibilities of a Creator are:
\begin{itemize}
\item provide the necessary data to the \msrprojectname system for its initialization.
\end{itemize}
\subsection{Activator}
An activator is a logical representation of the active part the \msrprojectname system.
It represents an implicit stakeholder belonging to the system's environment that
interacts with the \msrprojectname system autonomously without the need of a external
entity. It is usually used for representing time triggered functionalities. The
objectives of a activator are:
\begin{itemize}
\item to communicate the current time to the system
\item to notify the administrator that some crisis are still pending for a too
 long time.
\end{itemize}
In order to achieve these objectives, the responsibilities of a activator are:
\begin{itemize}
\item to know the current universal time
\item to send the messages to the system according to the time constraints
 specifically defined for it.
\end{itemize}
\newpage

\section{System's Actors}
The objective of this section is not to provide the full requirement elicitation
document in this section but to reuse a part of this document to provide a
informal introduction to the Messir specification of the system under
development. The use case model is made of a use case diagrams modelling
abstractly and informally the actors and their use cases together with a set of
use cases descriptions. In addition, those diagrams and description tables are
adapted to the Messir specification since actor and messages names together with
parameters are partly adapted to be consistent with the specification
identifiers. Among all the stakeholders presented in the previous section, we
can determine five types of direct actors:
\begin{itemize}
	\item actComCompany: for the Communication Company stakeholder.
	\item actAdministrator: for the Administrator stakeholder.
	\item actCoordinator: for the Coordinators stakeholders.
	\item actActivator: for the Activator stakeholder.
	\item actMsrCreator: for the Creator stakeholder.
\end{itemize}
In addition to those system actors, we can add five other types of actors
related to the systems ones. Those five actors are grouped into two categories:
\begin{itemize}
	\item \textit{Indirect actors}
		\begin{itemize}
			\item \textit{Witness}: for any human that is a witness of a car crash
			\item \textit{Victim}: for any human that is a victim of a car crash
			\item \textit{Anonymous}: for any human that want to inform about a car crash
			while staying anonymous.
		\end{itemize}
	\item \textit{Abstract actors}
		\begin{itemize}
			\item actHuman: represent abstractly any kind of human being actor wanting to
			communicate with the ABC system in the context of a car crash.
			\item actAuthenticated: for the logical Activator stakeholder.
		\end{itemize}
\end{itemize}
The objective of this section is not to provide the full requirement elicitation
document in this section but to reuse a part of this document to provide a
informal introduction to the \msrmessir specification of the system under
development. The use case model is made of a use case diagrams modelling
abstractly and informally the actors and their use cases together with a set of
use cases descriptions.
In addition, those diagrams and description tables are adapted to the \msrmessir
specification since actor and messages names together with parameters are partly
adapted to be consistent with the specification identifiers (see
\cite{messirbook} for more details).


